---
title: "Assg_3a"
author: "Yesdi Calvin, Aulia Dini"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### GitHub link: https://github.com/aulia0716/Group17_Assignment3.git

### Library

```{r, message=FALSE, warning=FALSE}
library(xml2)
library(rvest)
library(tidyverse)
library(xml2)
library(rvest)
library(jsonlite)
library(robotstxt)
library(RSocrata)
library(curl)
```

### Web Scraping

In this assignment, your task is to scrape some information from Wikipedia. We start with the following page about Grand Boulevard, a Chicago Community Area.

https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago

The ultimate goal is to gather the table "Historical population" and convert it to a data.frame.

As a first step, read in the html page as an R object. Extract the tables from this object (using the rvest package) and save the result as a new object. Follow the instructions if there is an error. Use str() on this new object, it should be a list. Try to find the position of the "Historical population" in this list since we need it in the next step.

Extract the "Historical population" table from the list and save it as another object. You can use subsetting via [[…]] to extract pieces from a list. Print the result.

You will see that the table needs some additional formatting. We only want rows and columns with actual values (I called the table object pop).

```{r}
# read the path
paths_allowed("https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago")
```

```{r}
# read the html
site <- read_html("https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago")
site
```
```{r}
# Extract the tables from the HTML page
tables <- site %>% html_table(fill = TRUE)
tables
```

```{r}
# Use str() on this new object to display the structure of the tables
#str(tables)
```

```{r}
# Extract the "Historical population" table from the list
pop0 <- tables[[2]]
pop0
```

```{r}
# We only want rows and columns with actual values. So, it needs some additional formatting. 
pop <- pop0[2:10,-3]
print(pop)
```

### Expanding to More Pages

That's it for this page. However, we may want to repeat this process for other community areas. The Wikipedia page https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago has a section on "Places adjacent to Grand Boulevard, Chicago" at the bottom. Can you find the corresponding table in the list of tables that you created earlier? Extract this table as a new object.

```{r}
# Extract the "Places adjacent to Grand Boulevard, Chicago" from the list
adj_city <- tables[[3]]
```

```{r}
# Extract only the cells of the relevant column from the table
adj_city_east <- adj_city[3]
print(adj_city_east)
```

We want to use this list to create a loop that extracts the population tables from the Wikipedia pages of these places. To make this work and build valid urls, we need to replace empty spaces in the character vector with underscores. This can be done with gsub(), or by hand. The resulting vector should look like this: "Oakland,_Chicago" "Kenwood,_Chicago" "Hyde_Park,_Chicago".

```{r}
# Remove the first row containing "Armour Square, Chicago"
adj_city_east1 <- adj_city_east[-which(adj_city_east == "Armour Square, Chicago"), ]

# Define the values to keep
adj_city_east1 <- c("Oakland, Chicago", "Kenwood, Chicago", "Hyde Park, Chicago")

# Remove any leading or trailing whitespace
adj_city_c <- trimws(adj_city_east1)
adj_city_c <- gsub("^\\d+\\s+", "", adj_city_c)

# Replace spaces with underscores in the community area names
adj_city_c <- gsub(" ", "_", adj_city_c)

# Print the result
print(adj_city_c)
```

To prepare the loop, we also want to copy our pop table and rename it as pops. In the loop, we append this table by adding columns from the other community areas.

Build a small loop to test whether you can build valid urls using the vector of places and pasting each element of it after https://en.wikipedia.org/wiki/ in a for loop. Calling url shows the last url of this loop, which should be https://en.wikipedia.org/wiki/Hyde_Park,_Chicago.

```{r}
# Check the loop for the url
 for(i in adj_city_c) {
   url <- paste0("https://en.wikipedia.org/wiki/",i, sep = "")
   }
 url
```

Finally, extend the loop and add the code that is needed to grab the population tables from each page. Add columns to the original table pops using cbind().

```{r}
# build the loop 
# Create a list to store the data frames
pop_list <- list()

for(i in adj_city_c) {
  
  # access the link
  url <- paste0("https://en.wikipedia.org/wiki/",i, sep = "") 
  site <- read_html(url)
  print(url)
  
  # grab the tables
  tables <- site %>% html_table(fill = TRUE)
  
  # pick the population table
  pop0 <- tables[[2]]
  
  # clean the table
  pop <- pop0[2:10,-3]
  
  # Store the data frame in the list
  pop_list[[i]] <- pop
  
}

# Combine the data frames in the list using cbind
pops <- do.call(cbind, pop_list)

# print the result
pops
```


### Scraping and Analyzing Text Data

Suppose we wanted to take the actual text from the Wikipedia pages instead of just the information in the table. Our goal in this section is to extract the text from the body of the pages, then do some basic text cleaning and analysis.

First, scrape just the text without any of the information in the margins or headers. For example, for "Grand Boulevard", the text should start with, "Grand Boulevard on the South Side of Chicago, Illinois, is one of the …". Make sure all of the text is in one block by using something like the code below (I called my object description).

Using a similar loop as in the last section, grab the descriptions of the various communities areas. Make a tibble with two columns: the name of the location and the text describing the location.

```{r}
# Build the loop
# Initialize an empty tibble to store the information
city_data <- tibble(City = character(0), Description = character(0))

for (i in adj_city_c) {
  
  # grab the information from the url
  url <- paste0("https://en.wikipedia.org/wiki/", i, sep = "") 
  site <- read_html(url)
  nds <- html_elements(site, xpath = '//p')
  names <- html_text(nds) %>% paste(collapse = ' ')
  
  # Create a tibble for the current city and append it to city_data
  city_info <- tibble(City = i, Description = names)
  city_data <- bind_rows(city_data, city_info)
}

# Print the final tibble
print(city_data)
```

Let's clean the data using tidytext. If you have trouble with this section, see the example shown in https://www.tidytextmining.com/tidytext.html

```{r}
# Install the library
library(tidytext)
```

Create tokens using unnest_tokens. Make sure the data is in one-token-per-row format. Remove any stop words within the data. What are the most common words used overall?

Plot the most common words within each location. What are some of the similarities between the locations? What are some of the differences?

```{r}
# create token using `unnest_token`
tidy_city <- city_data %>%
  unnest_tokens(Description, Description, token = "words")
head(tidy_city)
```

```{r, message=FALSE}
# Load stop words
data(stop_words)

# change the column names
names(tidy_city)[names(tidy_city) == "Description"] <- "word"

# Assuming you have a tibble called tidy_books in the one-word-per-row format
tidy_city2 <- tidy_city %>%
            anti_join(stop_words)

# Check the result
head(tidy_city2)
```

```{r}
# compute overall common words within each location
library(dplyr)
tidy_city3 <- tidy_city2 %>%
  count(word, sort = TRUE)

# print the result
head(tidy_city3)
```
 
```{r}
library(tidyverse)

tidy_city3 %>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)
```

The most common words with a frequency higher than thirty in Oakland, Kenwood, and Hyde Park community areas are `park`, `hyde`, `chicago`,  `street`, and `kenwood`. 

### Similarities and Difference among community areas (Just for communities in east of Grand Boulevard)

```{r}
library(tidyr)

# build the table
frequency <- tidy_city2 %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(City, word) %>%
  group_by(City) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = City, values_from = proportion) %>%
  pivot_longer(`Kenwood,_Chicago`:`Hyde_Park,_Chicago`, names_to = "City", values_to = "proportion")

# print the result
frequency
```

### Create plot 

```{r, message=FALSE, warning=FALSE}
library(scales)

# create the plot of words frequency
ggplot(frequency, aes(x = proportion, y = `Oakland,_Chicago`, 
                      color = abs(`Oakland,_Chicago` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~City, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Oakland,_Chicago", x = NULL)
```

The word close to the plot line shows the similar frequency between the two cities. Based on the graph, `Chicago` is the most common word, with the highest frequency in each community area (Oakland, Hyde Park, and Kenwood). `Boulevard` is the least common word in the three communities. 

`African`, `American`, and `rest` are common words between Oakland and Hyde Park. The word `community`, `avenue`, `cottage`, `center`, and `boulevard` are common words between Oakland and Kenwood. Additionally, only in Hyde Park the words `apartment`, `house`, and `park` have a high frequency. `housing`, `constructed`, `church`, and `beginning` are words with high frequency only in Oakland. Furthermore, `Kenwood` and `annexed` are words with high frequency only in Kenwood. 

### Compute correlation test between Hyde Park and Oakland

```{r}
# Subset the data for the current city
  city_data <- frequency[frequency$City == "Hyde_Park,_Chicago", ]
  
# Perform the correlation test
  cor_test_result <- cor.test(data = city_data, ~ proportion + `Oakland,_Chicago`)
  
# Print the result 
  cor_test_result
```

The correlation value of word frequency between Oakland and Hyde Park shows a relatively high and positive  with a score of 0.7. All of the correlation shows a statistically significant result. It means that the words with high frequency in Oakland tend to have a high frequency in Hyde Park. 

### Compute correlation test between Kenwood and Oakland

```{r}
# Subset the data for the current city
  city_data <- frequency[frequency$City == "Kenwood,_Chicago", ]
  
# Perform the correlation test
  cor_test_result <- cor.test(data = city_data, ~ proportion + `Oakland,_Chicago`)
  
# Print the result 
  cor_test_result
```

The correlation value of word frequency between Oakland and Kenwood is 0.5. The correlation value has a moderate, significant, and positive score. It means that the words with high frequency in Oakland tend to have a high frequency in Kenwood. 

### Check correlation between Kenwood and Hyde Park

```{r}
# Subset the data for the two cities
city_data_kenwood <- frequency[frequency$City == "Kenwood,_Chicago", ]
city_data_hyde_park <- frequency[frequency$City == "Hyde_Park,_Chicago", ]

# Perform the correlation test
cor_test_result <- cor.test(city_data_kenwood$proportion, city_data_hyde_park$proportion)

# Print the result
print(cor_test_result)
```
The correlation value of word frequency between Hyde Park and Kenwood is 0.5. The correlation value has a moderate, significant, and positive score. It means that the words with high frequency in Hyde Park tend to have a high frequency in Kenwood.
