---
title: "Assg_3a"
author: "Yesdi Calvin, Aulia Dini"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### GitHub link: https://github.com/aulia0716/Group17_Assignment3.git

### Library

```{r, message=FALSE, warning=FALSE}
library(xml2)
library(rvest)
library(tidyverse)
library(xml2)
library(rvest)
library(jsonlite)
library(robotstxt)
library(RSocrata)
library(curl)
```

### Web Scraping

In this assignment, your task is to scrape some information from Wikipedia. We start with the following page about Grand Boulevard, a Chicago Community Area.

https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago

The ultimate goal is to gather the table "Historical population" and convert it to a data.frame.

As a first step, read in the html page as an R object. Extract the tables from this object (using the rvest package) and save the result as a new object. Follow the instructions if there is an error. Use str() on this new object, it should be a list. Try to find the position of the "Historical population" in this list since we need it in the next step.

Extract the "Historical population" table from the list and save it as another object. You can use subsetting via [[…]] to extract pieces from a list. Print the result.

You will see that the table needs some additional formatting. We only want rows and columns with actual values (I called the table object pop).

```{r}
# read the path
paths_allowed("https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago")
```

```{r}
# read the html
site <- read_html("https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago")
site
```
```{r}
# Extract the tables from the HTML page
tables <- site %>% html_table(fill = TRUE)
tables
```

```{r}
# Use str() on this new object to display the structure of the tables
#str(tables)
```

```{r}
# Extract the "Historical population" table from the list
pop0 <- tables[[2]]
pop0
```

```{r}
# We only want rows and columns with actual values. So, it needs some additional formatting. 
pop <- pop0[2:10,-3]
print(pop)
```

### Expanding to More Pages

That's it for this page. However, we may want to repeat this process for other community areas. The Wikipedia page https://en.wikipedia.org/wiki/Grand_Boulevard,_Chicago has a section on "Places adjacent to Grand Boulevard, Chicago" at the bottom. Can you find the corresponding table in the list of tables that you created earlier? Extract this table as a new object.

```{r}
# Extract the "Places adjacent to Grand Boulevard, Chicago" from the list
adj_city <- tables[[3]]
```

```{r}
# Extract only the cells of the relevant column from the table
adj_city_east <- adj_city[3]
print(adj_city_east)
```

We want to use this list to create a loop that extracts the population tables from the Wikipedia pages of these places. To make this work and build valid urls, we need to replace empty spaces in the character vector with underscores. This can be done with gsub(), or by hand. The resulting vector should look like this: "Oakland,_Chicago" "Kenwood,_Chicago" "Hyde_Park,_Chicago".

```{r}
# Remove the first row containing "Armour Square, Chicago"
adj_city_east1 <- adj_city_east[-which(adj_city_east == "Armour Square, Chicago"), ]

# Define the values to keep
adj_city_east1 <- c("Oakland, Chicago", "Kenwood, Chicago", "Hyde Park, Chicago")

# Remove any leading or trailing whitespace
adj_city_c <- trimws(adj_city_east1)
adj_city_c <- gsub("^\\d+\\s+", "", adj_city_c)

# Replace spaces with underscores in the community area names
adj_city_c <- gsub(" ", "_", adj_city_c)

# Print the result
print(adj_city_c)
```

To prepare the loop, we also want to copy our pop table and rename it as pops. In the loop, we append this table by adding columns from the other community areas.

Build a small loop to test whether you can build valid urls using the vector of places and pasting each element of it after https://en.wikipedia.org/wiki/ in a for loop. Calling url shows the last url of this loop, which should be https://en.wikipedia.org/wiki/Hyde_Park,_Chicago.

```{r}
# Check the loop for the url
 for(i in adj_city_c) {
   url <- paste0("https://en.wikipedia.org/wiki/",i, sep = "")
   }
 url
```

Finally, extend the loop and add the code that is needed to grab the population tables from each page. Add columns to the original table pops using cbind().

```{r}
# build the loop 
# Create a list to store the data frames
pop_list <- list()

for(i in adj_city_c) {
  
  # access the link
  url <- paste0("https://en.wikipedia.org/wiki/",i, sep = "") 
  site <- read_html(url)
  print(url)
  
  # grab the tables
  tables <- site %>% html_table(fill = TRUE)
  
  # pick the population table
  pop0 <- tables[[2]]
  
  # clean the table
  pop <- pop0[2:10,-3]
  
  # Store the data frame in the list
  pop_list[[i]] <- pop
  
}

# Combine the data frames in the list using cbind
pops <- do.call(cbind, pop_list)

# print the result
pops
```

